---
title: "GenomeInfoDb: Submitting your organism to GenomeInfoDb"
author: "Sonali Arora"
date: "Modified: 16 January, 2013. Compiled: `r format(Sys.time(), '%B %d, %Y')`"
vignette: >
   %\VignetteIndexEntry{GenomeInfoDb: Submitting your organism to GenomeInfoDb}
   %\VignetteDepends{}
   %\VignetteKeywords{organism, GenomeInfoDb}
   %\VignettePackage{GenomeInfoDb}
   %\VignetteEngine{knitr::knitr}
   %\VignetteEngine{knitr::rmarkdown}
   %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
---

This document is meant for package developers wanting to submit an
organism which does not already exist in [_GenomeInfDb_](https://bioconductor.org/packages/3.16/bioc/html/GenomeInfoDb.html), to be a part of [_GenomeInfDb_](https://bioconductor.org/packages/3.16/bioc/html/GenomeInfoDb.html).

# Background

[_GenomeInfDb_](https://bioconductor.org/packages/3.16/bioc/html/GenomeInfoDb.html) provides a multitude of functions to subset and access seqName mappings
and styles associated with an organism. One can use the supplementary
manual \"GenomeInfoDb.pdf\" to see such functions. Alternately if there
is no support for an organism for one's choice, one can submit a tab
delimited file (as detailed by the sections below) to request their
favorite organism to become a part of GenomeInfoDb package.

# Support for existing organisms

GenomeInfoDb already provides support for a multitude of organisms, to
see a detailed list of organism and the supported seqname styles
associated with those organism, one can simply run :


```{r verbatim, message=FALSE}
library(GenomeInfoDb)
names(genomeStyles())
```

# File format for new organism

If your favorite organism does not exist in the above list, one can
submit a tab-delimited file in the following format and request for your
organism to be added to [_GenomeInfDb_](https://bioconductor.org/packages/3.16/bioc/html/GenomeInfoDb.html)

1.  The file name should be in the following format:

2.  The columns should be tab-delimited in the following order

    -   circular

    -   auto

    -   sex

    -   1 column per seqname style and 1 row per chromosome name (not
        all chromosomes of a given organism necessarily belong to the
        mapping) where circular denotes all the circular chromosomes,
        auto denotes all the autosomes and sex denotes all the allosomes
        or sex chromosomes.

3.  The entries should be in T/F format for columns circular, auto and
    sex.

# Example File

One can look at existing organism files under
GenomeInfoDb/extdata/dataFiles in their R/library to get a further idea
about the format of files.

# Contacting us with your new file

Once your file is ready, Please send your file to:

```{r}
packageDescription("GenomeInfoDb")$Maintainer
```

